The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
newpage
clarify edges and nodes
minor edits, todos

@@

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were the social association network generated in
each season and landcover combination. Proximity-based social network layers
were generated using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].

@@

We altered social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
the spatial distance threshold required for group assignment (see above) and
re-assigned groups at incremental distance between 5-500m. For example, at the
finest social scale, only individuals within 5m of one another were considered
in the same group, whereas at the coarsest social scale, individuals within 500m
of one another were considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover classification map at varying scales relevant to caribou ecology.
We aggregated the 10m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
for caribou during foraging <!--(REF)-->, while re-sampling at 500m and 1000m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017).

### Temporal scale

We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (1 January)
and summer (3 August). The position of the time window was shifted by 1-48 days,
using a fixed time window length of 48 days. These new time windows were
iteratively used to partition data into two discrete seasons (winter, summer)
and generate multilayer networks.

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale by adjusting the time window, we investigated the influence of
the number of observations on resulting multilayer networks. We randomly
selected 500 timesteps and iteratively included 25 additional observations,
regenerating the multilayer network and calculating associations of individuals.
Subsequent iterations included the previous set of observations to mimic
observational data.

>>>>

\newpage

@@

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019].

@@

We altered the social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we modified
the spatial distance threshold required for group assignment using `spatsoc` [@Robitaille_2019] (see above) and
re-assigned groups at incremental distances between 5-500m. For example, at the
finest social scale, only individuals within 5m of one another were considered
in the same group, whereas at the coarsest social scale, individuals within 500m
of one another were considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology.
We aggregated the 10m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
for caribou during foraging <!--TODO: REF-->, while re-sampling at 500m and 1000m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017).

### Temporal scale
<!--TODO: are we missing some mention of 2017 summer and 2018 winter somewhere?-->
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (1 January)
and summer (3 August). The position of the time window was shifted by 1-48 days,
using a fixed time window length of 48 days. These new time windows were
iteratively used to partition data into two discrete seasons (winter, summer)
and generate multilayer networks.

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale by adjusting the time window, we investigated the influence of
the number of observations on resulting multilayer networks. We randomly
selected 500 timesteps and iteratively included 25 additional observations,
regenerating the multilayer network and calculating associations of individuals.
Subsequent iterations included the previous set of observations to mimic
observational data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
